02_LH-SIP_Quantification

### 2022-05-24 02_LH-SIP_Quantification.Rmd
corrected weighted turnover for mc data

    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_start_mc = mean(at2H_weighted_mc, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    f_t_mc = `2F_alk_mc_weighted`,

    dF_weighted = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),

    #Do the same for memory-corrected data:
    dF_weighted_mc = case_when(
      f_t_mc - f_start_mc >= 0 ~ f_t_mc - f_start_mc,
      f_t_mc - f_start_mc < 0 ~ 0),

  ) %>%
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted),
    # Do the same for memory corrected data
    u_d_mc_weighted = calculate_turnover(
      a = a,
      FT = f_t_mc,
      F0 = f_start_mc,
      FL = f_label,
      t = d_t
    ),
    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
  )
```

>>>>

    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_start_mc = mean(at2H_mn_zero_mc, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    f_t_mc = `2F_alk_mc_weighted`,

    # Calculate change in 2F:
    dF_weighted = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),

    # Calculate change in 2F (MC):
    dF_weighted_mc = case_when(
      f_t_mc - f_start_mc >= 0 ~ f_t_mc - f_start_mc,
      f_t_mc - f_start_mc < 0 ~ 0),

  ) %>%
  # Summarize:
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%

  # Calculate turnover:
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted),

    # Memory-corrected turnover:
    u_d_mc_weighted = calculate_turnover(
      a = a,
      FT = f_t_mc,
      F0 = f_start_mc,
      FL = f_label,
      t = d_t
    ),
    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
  )
```
